% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage [brazil]{babel}     % nomes e hifenaçã em português
 
\usepackage{t1enc}              % Permite digitar os acentos de forma normal
\usepackage[utf8]{inputenc} 

\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{\textit{Grazziella Gadotti}}

\address{Brighton, UK \\ gra.gadotti@gmail.com \\ Phone: +44 07405105756 \\ Post Code: BN21HF }
                           
                        
\begin{resume}                        
 
\section{Summary} A pharmacy graduate, currently attending to a MSc in Industrial Pharmaceutical Science.
Keen for a changing in career towards the Pharmaceutical Industrial field. Adaptable and dedicated
professional with a good interpersonal relationship. I’ve been fortunate enough to work in different
environments, companies and countries specially with customer service and pharmaceutical care.
 
\section{Education}
\textit{Sep 2015 – Sep 2016}\\
MSc in Industrial Pharmaceutical Science (Merit; Distinction), University of Brighton, United Kingdom.

\textit{Jan 2008 – Sep 2013}\\
Pharmacy and Clinical Analysis (2:1), Federal University of Santa Catarina, Brazil.

\section{Experience}

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Lidl Superstore Brighton (part-time)} \>\>\textbf{Jun 2015 - Present}\\
    \textit{Customer Assistant}\\        
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
To help in the master's expenses I’ve been working in a busy and multi-task team environment to provide
outstanding customer service, most of time under pressure.

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Dermus Compounding Pharmacy}    \>\>\textbf{Jun 2013 - Feb 2014}\\
    \textit{Pharmacist}\\        
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
Worked in the formulation, calculation and preparation of sublingual tablets. Assisted customers to achieve their
loyalty and selling targets applied by the company. Advised and answered physician’s questions regarding formulation
and doses. Worked with the formulation of solids, semi-solids, liquids and homeopathy.

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Federal University of Santa Catarina}    \>\>\textbf{Jul 2012 - Dec 2012}\\
    \textit{Lecturer’s assistant, Department of Microbiology}\\        
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
Assisted the lecturers during practical classes. Prepared materials, such as culture medias and maintained the
collection of bacteria, for the classes.

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Federal University of Santa Catarina}    \>\>\textbf{Mar 2012 - Jun 2012}\\
    \textit{Lecturer’s assistant, Department of Pharmacotechniques}\\        
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
Assisted lecturers during practical classes, as well as students by answering general questions about the subject.
Separated and organised materials and equipment necessary to the classes.

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Drugstore Oneda Ltda (Summer Job)}    \>\>\textbf{Dec 2012 - Jan 2012}\\
    \textit{Pharmacist}\\   
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
I was responsible for customer service and pharmaceutical care. I’ve worked in the book-keeping of controlled
medicines and stock control for orders.

\section{Skills Base}

			\textit{Languages}: Fluent in Portuguese, Professional working proficiency in English and Italian;
 
\section{More Info}

      \textit{Linkedin}: https://uk.linkedin.com/in/ggadotti/en


\end{resume}
\center{\LaTeX}
\end{document}









