% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage [brazil]{babel}     % nomes e hifenaçã em português
 
\usepackage{t1enc}              % Permite digitar os acentos de forma normal
\usepackage[utf8]{inputenc} 

\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{\textit{Claudinei Callegari}}

\address{Brazil, BR \\ cadicallegari@gmail.com \\ Phone: +55 (48) 9826 4067}
                           
                        
\begin{resume}                        
 
\section{Summary}       Bachelor in computer with background in software development. Full stack developer, working with
                        several tecnologies, such as C, Python, Ruby, and Lua. Expertise in Linux and Windows platform.
                        Great inter-personal relationship, team player and can-do attitude. Looking for new opportunities
                        and big challenges.                        
 
\section{Education}	Universidade Estadual do Oeste do Parana, BSc in Computer Science, December 2011.
  
\section{Experience}

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{DBA}    \>\>\textbf{May 2013 - Present}\\
    \textit{Software Engineer - Full Stack}\\        
    \textbf{Main Technologies}: Linux, Git, Python, Ruby, JavaScript, Web, Java, Android;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
    Team player of Parking Meter System project, responsbile for the web component where the backend is developed in Ruby
    and frontend CSS, JavaScript and HTML. Android application development. Deployment of Git versioning and continuous 
    integration servers
        
\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Digitro}    \>\>\textbf{Sep 2012 - May 2013}\\
    \textit{Software Engineer}\\        
    \textbf{Main Technologies}: Linux, Windows, C, SDL;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
    Development and maintenance of C applications using Specification and Description Language (SDL).
    
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Nexxera}    \>\>\textbf{Jul 2012 - Sep 2012}\\
    \textit{Software Engineer}\\   
    \textbf{Main Technologies}: Linux and Python;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
    Development using Python to handle, convert and store files data. Convert files "layouts" using a closed tool;
   
   %\vspace{20mm}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.5in}\= \kill % set up two tab positions
    \textbf{Ahgora}    \>\>\textbf{Jan 2012 - Jul 2012}\\
    \textit{Jr Software Engineer}\\   
    \textbf{Main Technologies}: C, Lua, Linux and Java(Android);
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
       Embedded systems development using C and Lua. Android development.
       
   %\vspace{20mm}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.5in}\= \kill % set up two tab positions
    \textbf{ITAI}    \>\>\textbf{May 2009 - Nov 2011}\\
    \textit{Trainee}\\   
    \textbf{Main Technologies}: Linux, C/C++ and Java;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
       Development with languages C, C++ e Java. Comunication between C and Java using SUN-RPC, JSON. Used Valgrind, Libxml2, Glib

\section{Skills Base}  \textit{Operating System}:  Linux (Debian, Ubuntu, CentOS), Windows NT/XP/Vista/7 and OSX;

			\textit{Networkings}: TCP/IP protocol suite;
  
			\textit{Progamming Languages}: C, Pascal, Python, Ruby, JavaScript, plus some experience with Lua and Java;
  
			\textit{Virtualization}: VirtualBox, VMWare, plus some experience with Xen;

			\textit{Languages}: Fluent in Portuguese, Intermediate in English and Spanish;
 
\section{More Info}
    \begin{itemize}
        \item \textbf{Linkedin}: https://www.linkedin.com/pub/claudinei-callegari/35/b71/a5b/en
         \item \textbf{Github}: https://github.com/cadicallegari
    \end{itemize}


\end{resume} 
\end{document}









