\documentclass[margin]{res}
\usepackage [brazil]{babel}
 
\usepackage{t1enc}
\usepackage[utf8]{inputenc} 

\topmargin=-0.5in
\setlength{\textheight}{10in}
\begin{document}  
\name{\textit{Samyra Cury Salek}}

\address{Brighton, UK \\ samyracsalek@gmail.com \\ Phone: +44 7305 759339 \\ Post Code: BN1 3TP }
                        
\begin{resume}                        

\section{Summary}

I am a self-motivated master graduate with 7 years of professional and
volunteer experience seeking a customer facing position in a company that
wishes to create and improve processes. I enjoy tackling challenges with
strong communication, leadership and research skills, aiming to increase
visibility and profit.

\section{Education}
\textit{2015 – 2018}\\
Karlshochschule International University, Karlsruhe, Germany , MA in Management.

\textit{2013 – 2014}\\
ESB Business School, Reutlingen, Germany, International Business Course.

\textit{2006 – 2007}\\
Georgetown University, Washington DC, USA, Communicative Skills Seminar.

\textit{2003 – 2009}\\
Pontifícia Universidade Católica de Campinas, Campinas, Brazil, BSc in Tourism.

\section{Experience}

\vspace{-0.1in}
    \begin{tabbing}
        \hspace{2.3in}\= \hspace{1.7in}\= \kill
        \textbf{Basepoint Business Centre} \>\>\textbf{Sep 2018 - Present}\\
        \textit{Community Manager}\\        
    \end{tabbing}\vspace{-20pt}
    \vspace{2mm}
    \begin{itemize}
        \item Active develop and maintain effective relationships with customers, teams and suppliers.
        \item Ensure the achievement of the centre financial goals and objectives.
        \item Develop, implementation and maintain all social media and marketing action.   
    \end{itemize}

\vspace{-0.1in}
    \begin{tabbing}
        \hspace{2.3in}\= \hspace{1.7in}\= \kill
        \textbf{Trend in Africa} \>\>\textbf{Aug 2015 - Jul 2018}\\
        \textit{Project Manager}\\        
    \end{tabbing}\vspace{-20pt}
    \vspace{2mm}
    \begin{itemize}
        \item Manage 170,000 euros donated by the Volkswagen Foundation (Volkswagen Stiftung) for a 3-year project;
        \item Courses and workshops organization in different African countries.
        \item Multitask role ranging from students’ applications, design of course schedule to engaging with community relationship, lecturers and suppliers from different countries.
        \item Development and implementation of all courses activities ensuring positive local social impact.
    \end{itemize}

\vspace{-0.1in}
    \begin{tabbing}
        \hspace{2.3in}\= \hspace{1.7in}\= \kill
        \textbf{TUBEX Holding} \>\>\textbf{Aug 2014 - Feb 2017}\\
        \textit{Account Manager}\\        
    \end{tabbing}\vspace{-20pt}
    \vspace{2mm}
    \begin{itemize}
        \item Daily management of client’s relationship and satisfaction.
        \item Responsible for projects reports, setting management client success targets between Brazil and Germany sites.
        \item Develop of internal and external documentation (score cards, CSR, CDP and Environmental Reports), increasing business opportunities with companies such as L’Oréal Paris, Natura \&Co and Beiersdorf AG.
    \end{itemize}    

\vspace{0.9in}
    \begin{tabbing}
        \hspace{2.3in}\= \hspace{1.7in}\= \kill
        \textbf{International Partnership of Business School} \>\>\textbf{May 2014 - Oct 2014}\\
        \textit{Assistant Marketing Manager}\\        
    \end{tabbing}\vspace{-20pt}
    \vspace{2mm}
    \begin{itemize}
        \item Processing of prospective master students’ applications.
        \item Construction and maintenance of student’s profile and information databases.
        \item Management of social media presence (e.g. Facebook, LinkedIn) with advertisement and creation of newsfeed groups
    \end{itemize}

\vspace{-0.1in}
    \begin{tabbing}
        \hspace{2.3in}\= \hspace{1.7in}\= \kill
        \textbf{Luna Consulting} \>\>\textbf{May 2014 - Oct 2014}\\
        \textit{Staff Specialist}\\        
    \end{tabbing}\vspace{-20pt}
    \vspace{2mm}
    \begin{itemize}
        \item Owner of full-cycle recruiting process for multiple global business clients.
        \item Sourcing \& interviewing of technical roles candidates for clients.
        \item Management of online job posting and applicant tracking system.
    \end{itemize}
  
\vspace{-0.1in}
    \begin{tabbing}
        \hspace{2.3in}\= \hspace{1.7in}\= \kill
        \textbf{Meta Social Institute} \>\>\textbf{Jan 2013 - Jul 2013}\\
        \textit{Project Manager}\\        
    \end{tabbing}\vspace{-20pt}
    \vspace{2mm}
    Development and delivery of a social projects for integration of adults with Down
    syndrome, focusing on basic independent skills.

\vspace{-0.1in}
    \begin{tabbing}
        \hspace{2.3in}\= \hspace{1.7in}\= \kill
        \textbf{IBM Brazil} \>\>\textbf{Jan 2011 - May 2012}\\
        \textit{Assistant Project Manager}\\        
    \end{tabbing}\vspace{-20pt}
    \vspace{2mm}
    \begin{itemize}
        \item Member of the team responsible for Delta Airlines business account.
        \item Support to project managers around the world, being the focal point for assigning all professionals to their projects.
        \item Mediator of meetings, responsible for weekly and monthly financial reports and projects progress worldwide.
        \item Assisting strategic projects decisions and implementations.
    \end{itemize}

\section{Strengths}
    \begin{itemize}
        \item Extend project management; quick to pick up new things and teach others
        \item Communicative, highly organised, honest, creative and collaborative with the team
        \item Strong computer skills, including MS Office
        \item Strong data and fact-based analysis
        \item Good written and verbal communication skills
    \end{itemize}

\section{Skills Base}
	\textit{Languages}: Fluent in Portuguese and English. Proficient in Spanish and German;
 
\section{More Info}
    \textit{Linkedin}: https://www.linkedin.com/in/samyra-salek-851a1265/

\end{resume} 
\end{document}
